Hypertension and microbiome

### 2019-05-15 articletwo.Rmd
Bigger plots

```{r abund salt lm continuous checks plot, fig.width=12, fig.height=8}
gvlma.table.plot(lm.lacto.duna)$plot %>% plot
```

@@

```{r abund salt lm group checks plot, fig.width=12, fig.height=8}
gvlma.table.plot(lm.lacto.saltgroup)$plot %>% plot
```

>>>>

```{r abund salt lm continuous checks plot, fig.width=12, fig.height=14}
gvlma.table.plot(lm.lacto.duna)$plot %>% plot
```

@@

```{r abund salt lm group checks plot, fig.width=12, fig.height=14}
gvlma.table.plot(lm.lacto.saltgroup)$plot %>% plot
```
